To Do List

### 2020-09-30 BMC_Genome_Biology_submission/cover_letter_Genome_Biology.Rmd
Final notes

We are submitting our manuscript "preciseTAD: A machine learning framework for precise 3D domain boundary prediction at base-level resolution" to be considered for the special issue "Regulatory Elements" in _Genome Biology_. This manuscript will be of interest to the community studying the regulatory associations within the three-dimensional (3D) genome structure.

@@

- The provided models pre-trained on Arrowhead-called TAD boundaries and Peakachu-called loop boundaries can predict domain boundaries in cells without Hi-C data using only genomic annotation data.

@@

- Transcription factors, spatial relationships (distance within the linear genome) between them and boundaries, random under-sampling are the critical features needed for accurate boundary predictions.

@@

- Biological properties of domain boundaries predicted using *preciseTAD* include the highest genomic signal of CTCF and other transcription factors, closer proximity to other genomic signatures, and higher` conservation across cell lines.

@@

In summary, our systematic machine learning framework evaluates previously overlooked properties of 3D interactions and 1D regulatory data, linking them into the most optimal model for domain boundary predictions. This improved precision in the domain boundary location will provide deeper insight into the association between genomic regulators and the 3D genome organization.

@@

With our best regards,  
On behalf of all authors,

@@

>>>>

We are submitting our manuscript "preciseTAD: A machine learning framework for precise 3D domain boundary prediction at base-level resolution" to be considered for the special issue "Regulatory Elements" in _Genome Biology_. This manuscript will be of interest to the community studying the regulatory associations with the three-dimensional (3D) genome structure.

@@

- The pre-trained models provided with the package can predict domain boundaries in cells without Hi-C data using only genomic annotation data.

@@

- Transcription factors, spatial relationships (distance within the linear genome) between them and boundaries, random under-sampling are the critical considerations needed for accurate boundary predictions.

@@

- Biological properties of boundaries predicted using *preciseTAD* include the highest genomic signal of CTCF and other transcription factors, closer proximity to other genomic signatures, and higher` conservation across cell lines.

@@

In summary, our systematic machine learning framework evaluates previously overlooked properties of 3D and 1D data associations, linking them into the most optimal model for domain boundary predictions. This improved precision in the domain boundary location will provide deeper insight into the association between genomic regulators and the 3D genome organization.

@@

With our best regards,

@@

09/30/2020
